Finiteness in Cubical Type Theory

### 2020-01-27 paper.tex
fits on single page

Finally, thanks to extensionality provided to us by HoTT, and the computation
properties provided by CuTT, we can derive decidable equality on functions over
finite types.
We can also use functions in our proof search.
Here, for instance, is a automated procedure which finds the
\(\AgdaFunction{not}\) function on \(\mathbf{Bool}\), given a specification.
\ExecuteMetaData[agda/Data/Pauli.tex]{not-spec}
\section{Related Work}
The univalent foundations program is the main basis for this work
\cite{hottbook}.
In particular, our formalisation in section~\ref{topos} relied heavily on
\cite[chapter 10]{hottbook}, and \cite{rijkeSetsHomotopyType2015}, a paper which
contains much of the same material.

@@

\section*{Acknowledgement}
This work has been supported by the Science Foundation Ireland under the
following grant: 13/RC/2D94 to Irish Software Research Centre.
\bibliographystyle{splncs04}
\bibliography{bibliography.bib}
\end{document}

>>>>

Finally, we can derive decidable equality on functions over finite types.
We can also use functions in our proof search.
Here, for instance, is a automated procedure which finds the
\(\AgdaFunction{not}\) function on \(\mathbf{Bool}\), given a specification.
\ExecuteMetaData[agda/Data/Pauli.tex]{not-spec}
\section{Related Work}
The univalent foundations program is the main basis for this work
\cite{hottbook}.
In particular, our formalisation in section~\ref{topos} relied heavily on
\cite[chapter 10]{hottbook}, and \cite{rijkeSetsHomotopyType2015}, a paper which
contains much of the same material.

@@

\subsubsection*{Acknowledgement}
This work has been supported by the Science Foundation Ireland under the
following grant: 13/RC/2D94 to Irish Software Research Centre.
\bibliographystyle{splncs04}
\bibliography{bibliography.bib}
\end{document}
